\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage[utf8]{inputenc}  % Added for better character encoding support

% Adjust spacing
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

% Page setup
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Margin adjustments
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

% Document settings
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
  \item\small{
    {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
  \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & \textbf{\small #2} \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textit{\small#1} & \textit{\small #2} \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \item
  \begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & \textbf{\small #2}\\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

% List settings
\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% Header
\begin{center}
    {\Huge \scshape Manas Kumar Thakur} \\ \vspace{3pt}
    New Delhi, India \\ \vspace{3pt}
    \small 
    \href{tel:+919650376167}{\raisebox{-0.1\height}\faPhone\ \underline{+91 9650376167}} ~
    \href{mailto:thakurmanas168@gmail.com}{\raisebox{-0.2\height}\faEnvelope\ \underline{thakurmanas168@gmail.com}} ~
    \href{https://www.linkedin.com/in/manasthakur30}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/manasthakur30}} ~
    \href{https://github.com/Manas-thakur}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/Manas-thakur}}
    \vspace{-8pt}
\end{center}

% Education Section
\section{Education \& Achievements}
\resumeSubHeadingListStart
  \resumeSubheading
    {Bachelor of Technology in Computer Science(AIML)}{Expected Graduation: 2027}
    {Dronacharya College of Engineering}{CGPA: 7.5/10}
\resumeSubHeadingListEnd

% Experience Section
\section{Experience}
\resumeSubHeadingListStart
  \resumeSubheading
    {Backend Developer Intern}{Feb. 2025 -- May 2025}
    {OSS \& Consulting}{Remote, India}
    \resumeItemListStart
      \resumeItem{Designed and optimized relational database architecture to ensure scalability and efficiency.}
      \resumeItem{Developed and managed database schemas using PostgreSQL, enforcing best practices in normalization and indexing.}
      \resumeItem{Implemented query optimization techniques, reducing query execution time and improving system performance.}
      \resumeItem{Designed and developed RESTful APIs for seamless database interactions, ensuring secure and efficient data handling.}
      \resumeItem{Integrated secure authentication mechanisms, including JWT tokens and OAuth, ensuring data protection.}
      \resumeItem{Collaborated with backend and cloud teams to streamline data flow across distributed systems using AWS and GCP.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

% Technical Projects Section
\section{Technical Projects}
\resumeSubHeadingListStart
  \resumeProjectHeading
    {\textbf{SIH 2023 - Lithology Project} $|$ Machine Learning, Computer Vision}{December 2023}
    \resumeItemListStart
      \resumeItem{Developed an intelligent system for real-time object detection and classification using machine learning and computer vision.}
      \resumeItem{Utilized a multi-language approach, with the primary codebase in JavaScript, Python, Jupyter Notebook, and C++.}
      \resumeItem{Implemented advanced detection techniques to enhance accuracy and reliability in object classification.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{IDE 2024 - ML for Construction Progress Monitoring} $|$ Deep Learning, OpenCV, Python}{August 2024}
    \resumeItemListStart
      \resumeItem{Built a real-time ML-powered system for tracking construction progress through automated image analysis.}
      \resumeItem{Implemented an anomaly detection module to flag inconsistencies and prevent reporting errors.}
      \resumeItem{Enhanced efficiency by reducing reliance on manual progress tracking and improving data accuracy.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Buildspace - Pothole Detection and GPS Tagging} $|$ YOLO, OpenCV, GPS API, Python}{September 2024}
    \resumeItemListStart
      \resumeItem{Developed a real-time pothole detection system using YOLO and OpenCV to identify road defects.}
      \resumeItem{Integrated GPS tagging to map detected potholes, providing precise location data for road maintenance teams.}
      \resumeItem{Optimized the system for deployment in smart city infrastructure to improve road safety.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Building Thoughts - AI-Powered Diary} $|$ Ongoing}{}
    \resumeItemListStart
      \resumeItem{Developing an AI-powered diary that interacts with users, responding intelligently to their entries.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

% Technical Skills Section
\section{Technical Skills}
\resumeSubHeadingListStart
  \resumeItem{\textbf{Programming Languages:} Python, R, SQL, C, C++}
  \resumeItem{\textbf{Machine Learning \& AI:} Supervised/Unsupervised Learning, Deep Learning, Transfer Learning, Computer Vision, Object Detection, NLP, Reinforcement Learning}
  \resumeItem{\textbf{Frameworks \& Libraries:} PyTorch, TensorFlow, Scikit-learn, FastAI, OpenCV, YOLOv8, Hugging Face, LangChain, SentenceTransformers, OpenAI API}
  \resumeItem{\textbf{Model Architectures:} CNNs, RNNs, LSTMs, Transformers, U-Net, DINO, CLIP}
  \resumeItem{\textbf{Data Science \& Visualization:} Pandas, NumPy, Matplotlib, Seaborn, Plotly, Streamlit, Jupyter Notebook}
  \resumeItem{\textbf{MLOps \& Tools:} Weights \& Biases, MLflow, Docker, Git, CUDA, NVIDIA Jetson, CI/CD}
  \resumeItem{\textbf{Databases \& Vector Stores:} PostgreSQL, MongoDB, Redis, LanceDB, Pinecone}
\resumeSubHeadingListEnd


% Leadership \& Achievements Section
\section{Leadership \& Achievements}
\resumeSubHeadingListStart
  \resumeItem{\textbf{Smart India Hackathon Winner:} SIH 2023 Winner, Automated lithology classification using AI and deep learning.}
  \resumeItem{\textbf{Engineers Day Idea Competition(DCE):} Secured second place for designing a fire-resistant system for car accidents.}
  \resumeItem{\textbf{IDE Bootcamp Selection:} Advanced to Phase 2 at Amity University Rajasthan, collaborating on innovations.}
  \resumeItem{\textbf{AI Team - Deviators Club:} Worked on AI/ML projects, gaining hands-on experience in advanced technologies.}
\resumeSubHeadingListEnd


\end{document}
